### 2013-04-09 exam6/2.tex
update ec problem

>>>>

\begin{solution}
\begin{verbatim}
//> 5pts all correct
//> Ok if they have another implementation if it's right

// in BST<X> interface
    // Add all elements of this BST to ls, in order.
    void addTo(ArrayList<X> ls);

// in ABST<X>
    public Iterator<X> iterator() {
        ArrayList<X> elems = new ArrayList<X>();
        this.addTo(elems);
        return elems.iterator();
    }

// in Leaf<X>
    public void addTo(ArrayList<X> ls) {}

// in Node<X>
    public void addTo(ArrayList<X> ls) {
        this.left.addTo(ls);
        ls.add(this.x);
        this.right.addTo(ls);
    }
\end{verbatim}
\end{solution}
